---
title: "Lab 15: Likelihood Ratio Tests"
output:
  pdf_document:
    keep_tex: true
header-includes:
   - \usepackage{booktabs}
geometry: margin=1.5cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

Let's continue the likelihood ratio test example from the handout on April 20.  As a reminder, here is our set up:

$X_1, \ldots, X_5 \sim \text{Normal}(\theta, 5^2)$

We want to test the hypotheses

$H_0: \theta = 25$
$H_A: \theta = 10$

Suppose we observe a sample mean of $\bar{x} = 20$ based on a sample of $n = 5$ observations.

#### (a) Suppose the null hypothesis of the test is true.  What is the distribution of the sample mean $\bar{X}$?

$\bar{X} \sim \text{Normal}(25, 5)$

The mean is from the null hypothesis specification.  Note that the variance was divided by 5.

#### (b) Find the p-value for the likelihood ratio test.

```{r}
pnorm(20, mean = 25, sd = sqrt(5))
```

#### (c) Suppose that the alternative hypothesis is $H_A: \theta = 0$ instead of $H_A: \theta = 10$.  Would the p-value for the test change?  You don't need to actually calculate a p-value.  Justify your answer in a few words.

The p-value would be the same because the form of the p-value calculation for this test is determined only by whether the value of $\theta$ in the alternative hypothesis is less than the value from the null hypothesis or greater than it.

#### (d) How about if the alternative hypothesis was $H_A: \theta = 20$.  Would the p-value for the test change?  You don't need to actually calculate a p-value.  Justify your answer in a few words.

The p-value would be the same because the form of the p-value calculation for this test is determined only by whether the value of $\theta$ in the alternative hypothesis is less than the value from the null hypothesis or greater than it.

#### (e) How about if the alternative hypothesis was $H_A: \theta = 25.1$.  Would the p-value for the test change?  You don't need to actually calculate a p-value.  Justify your answer in a few words.

The p-value would be different because in this case the value of $\theta$ specified in the alternative hypothesis is greater than the value of $\theta$ specified in the null hypothesis.
